Correlations between gender and research topics at three major archaeology conferences

### 2020-07-17 analysis/paper/paper.Rmd
table10

In an article by @sinclair2016intellectual, he has compared the relative standings between men and women researchers in terms of number of citations made by other authors in the field of archaeology. Among the list of 50 most cited authors, only 6 of them (12%) are women, meaning that recognition in terms of citation are still mostly given to men, similar theme can be seen even if we increase to top 250 authors, with 19% being women [@sinclair2016intellectual]. <!-- add highs and lows for women percentag from table 10 -->  One possible reason could be that men and women simply have preferences over different topics and this is one reason why we want to examine if there's some correlation between gender and topics of presentation.

>>>>

In an article by @sinclair2016intellectual, he has compared the relative standings between men and women researchers in terms of number of citations made by other authors in the field of archaeology. Among the list of 50 most cited authors, only 6 of them (12%) are women, meaning that recognition in terms of citation are still mostly given to men, similar theme can be seen even if we increase to top 250 authors, with 19% being women [@sinclair2016intellectual]. After analyzing the most cited authors and their articles' thematic clusterings, it can be seen that there is relatively more women authors whose article is in the category of Archaeology of Early State Societies in the Americas (N and C America) with 46% women authors,the category of Archaeological chemistry (esp. lipids analysis) with 40% women authors, Isotope analysis with 30% women authors, and dating (esp. thermoluminescence and magnetics) with 30% women authors, while the average women author that are cited in the field of archaeology as a whole is around 14%. One possible reason could be that men and women simply have preferences over different topics and this is one reason why we want to examine if there's some correlation between gender and topics of presentation.
